Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-11-01 paper/paper.qmd
Rendered paper updated.

# Extract additional statistics
r_squared <- model_summary$r.squared
adj_r_squared <- model_summary$adj.r.squared
f_statistic <- model_summary$fstatistic[1]
residual_se <- model_summary$sigma

@@

@@

# Display the full summary table using kable
kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])
```

>>>>

# Extract additional statistics
r_squared <- model_summary$r.squared
adj_r_squared <- model_summary$adj.r.squared
f_statistic <- model_summary$fstatistic[1]
p_value <- pf(f_statistic, model_summary$fstatistic[2], model_summary$fstatistic[3], lower.tail = FALSE)
residual_se <- model_summary$sigma

@@

# Load necessary library
library(dplyr)

@@

# Display the full summary table using kable, excluding "F-statistic p-value" row
library(knitr)
kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])
```
